ANGSD-wrapper: utilities for analyzing next generation sequencing data

### 2016-01-15 manuscript.tex
edits

\usepackage[colorinlistoftodos]{todonotes}
\definecolor{flame}{rgb}{0.89, 0.35, 0.13}
%\setlength{\marginparwidth}{1.5cm}
\newcommand{\jri}[1]{\todo[size=\scriptsize, color=flame]{#1}}
\newcommand{\fst}{$\textrm{F_{\textrm{\scriptsize ST}}}$}          
\newcommand{\X}{\textcolor{red}{\bf X}}

@@

As a demonstration of analyses in ANGSD-wrapper, we explore patterns of diversity in a single genomic region of a subset of domesticated maize and wild teosinte. We used resequenced samples from the HapMap2 project  and calculated summary statistics using a 10 megabase region on chromosome 10 \citep{chia2012maize} . The data is available at \url{https://figshare.com/articles/Example_Data_tar_bz2/2063442}.

We first use the SFS method to estimate the site frequency spectrum (SFS) of both maize and its wild progenitor \textit{Zea mays} ssp. \textit{parviglumis}, assuming an inbreeding coefficient of $F=1$ since these are all highly inbred samples. %\jri{do we worry that fig. 3 not graphs directly from A-W?} % noted this in the figure legend, SFSes are basically from AW, just colors changed. In the future should we add color picker for SFS?

Consistent with previous results \citep{hufford2012comparative}, we show that the maize SFS is skewed towards more intermediate-frequency variants (Figure \ref{fig:figure3}A-B), likely a result of the bottleneck associated with maize domestication \citep{Beissinger031666}.
We find further evidence of the effect of domestication using the Thetas method, revealing lower levels overall levels of diversity in maize (Figure \ref{fig:figure3}C). These results use Tripsacum as an ancestral sequence, which was generated using the Ancestral Sequence method in ANGSD-wrapper. %\jri{fill in \X's with which A-W script we used. probably need to modify this to mention Tripsacum and generation of the ancestral seq. and which A-W script we used for that.} done
Using the 2DSFS method, which includes an \fst calculation, we then scan our example region for windows with elevated differentiation between maize and teosinte. 
The mean \fst in this region is 0.013, which is an order of magnitude lower than the genome-wide reported value of 0.11 \citep{hufford2012comparative}.   
The \X windows in the 1\% tail of highest \fst values include genes several genes identified as potential targets of selection during domestication in \citep{hufford2012comparative} \jri{see supp tables in Huff. make supp. table of genes in top 1\%. sorry to add, but this is cool \& demonstrates more stuff A-W can do. don't need a graph}

>>>>

\usepackage[colorinlistoftodos]{todonotes}
\definecolor{flame}{rgb}{0.89, 0.35, 0.13}
%\setlength{\marginparwidth}{1.5cm}
\newcommand{\jri}[1]{\todo[size=\scriptsize, color=flame]{#1}}
\newcommand{\fst}{${F_{ST}}$ }          
\newcommand{\X}{\textcolor{red}{\bf X}}

@@

As a demonstration of analyses in ANGSD-wrapper, we explore patterns of diversity in a single genomic region of a subset of domesticated maize and wild teosinte. We used resequenced samples from the HapMap2 project  and calculated summary statistics using a 10 megabase region on chromosome 10 \citep{chia2012maize}. The data is available at \url{https://figshare.com/articles/Example_Data_tar_bz2/2063442}. In the following we refer to methods listed in Table \ref{tab:methods} when describing analyses.

We first use the SFS method to estimate the site frequency spectrum (SFS) of both maize and its wild progenitor \textit{Zea mays} ssp. \textit{parviglumis}, assuming an inbreeding coefficient of $F=1$ for these highly inbred samples. 
Consistent with previous results \citep{hufford2012comparative}, we show that the maize SFS is skewed towards more intermediate-frequency variants (Figure \ref{fig:figure3}A-B), likely a result of the bottleneck associated with maize domestication \citep{Beissinger031666}.
We find further evidence of the effect of domestication using the Thetas method, revealing lower overall levels of diversity in maize (Figure \ref{fig:figure3}C). 
These results use a sample from the genus \textit{Tripsacum} as an ancestral sequence generated using the Ancestral Sequence method. 
Using the 2DSFS method, which includes an \fst calculation, we then scan our example region for windows with elevated differentiation between maize and teosinte. 
The mean \fst in this region is 0.013, which is an order of magnitude lower than the genome-wide reported value of 0.11 \citep{hufford2012comparative}.   
The \X windows in the 1\% tail of highest \fst values include genes several genes identified as potential targets of selection during domestication in \citep{hufford2012comparative}
